Should geophysicists use the gravity disturbance or the anomaly?

### 2018-07-03 manuscript/letter.tex
remove author identification and repository links

\address{
\footnotemark[1]Observat\'{o}rio Nacional, \\
Department of Geophysics, \\
Rio de Janeiro, Brazil \\
\footnotemark[2]University of Hawai'i at M\={a}noa, \\
Department of Geology and Geophysics, SOEST, \\
Honolulu, USA}
\author{Vanderlei C. Oliveira Jr\footnotemark[1], Leonardo Uieda\footnotemark[2],
Kristoffer A. T. Hallam\footnotemark[1] and Val\'{e}ria C. F. Barbosa\footnotemark[1]}

\footer{vanderlei@on.br, leouieda@gmail.com, kristoffer.hallam@gmail.com, valcris@on.br}
\lefthead{Oliveira Jr et al.}
\righthead{Gravity anomaly or gravity disturbance?}

@@

Because the centrifugal parts of both the normal gravity vector
and the Earth's gravity vector are equal,
the gravity disturbance vector $\delta \mathbf{g}_{P}$
represents a purely gravitational effect.
As a consequence of the superposition principal \citep{blakely1996},
this effect is caused by contrasts between
the internal density distributions
of the actual Earth and the normal Earth.
In applied geophysics, these density differences are generally called
\textit{anomalous masses} \citep[e.g.,][]{hammer1945,lafehr1965},
\textit{density anomalies} \citep[e.g.,][]{forsberg1984},
or \textit{gravity sources} \citep[e.g.,][]{blakely1996}.
Here, we opted for using the last term.

@@

\section{ACKNOWLEDGMENTS}

The authors would like to thank the editor and reviewers for their criticisms
and corrections. All source code and data used to generate the results presented 
here are available at
\href{https://doi.org/10.5281/zenodo.1255306}{doi.org/10.5281/zenodo.1255306}
and
\href{https://github.com/pinga-lab/use-the-disturbance}{github.com/pinga-lab/use-the-disturbance}.

>>>>

%remove author identification for double-blind review process
%\address{
%\footnotemark[1]Observat\'{o}rio Nacional, \\
%Department of Geophysics, \\
%Rio de Janeiro, Brazil \\
%\footnotemark[2]University of Hawai'i at M\={a}noa, \\
%Department of Geology and Geophysics, SOEST, \\
%Honolulu, USA}
%\author{Vanderlei C. Oliveira Jr\footnotemark[1], Leonardo Uieda\footnotemark[2],
%Kristoffer A. T. Hallam\footnotemark[1] and Val\'{e}ria C. F. Barbosa\footnotemark[1]}
%\footer{vanderlei@on.br, leouieda@gmail.com, kristoffer.hallam@gmail.com, valcris@on.br}
%\lefthead{Oliveira Jr et al.}

\righthead{Gravity anomaly or gravity disturbance?}

@@

Because the centrifugal parts of both the normal gravity vector
and the Earth's gravity vector are equal,
the gravity disturbance vector $\delta \mathbf{g}_{P}$
represents a purely gravitational effect.
As a consequence of the superposition principle,
this effect is caused by contrasts between
the internal density distributions
of the actual Earth and the normal Earth.
In applied geophysics, these density differences are generally called
\textit{anomalous masses} \citep[e.g.,][]{hammer1945,lafehr1965},
\textit{density anomalies} \citep[e.g.,][]{forsberg1984},
or \textit{gravity sources} \citep[e.g.,][]{blakely1996}.
Here, we opted for using the last term.

@@

%\section{ACKNOWLEDGMENTS}
%
%The authors would like to thank the editor and reviewers for their criticisms
%and corrections. All source code and data used to generate the results presented 
%here are available at
%remove author identification for double-blind review process
%\href{https://doi.org/10.5281/zenodo.1255306}{doi.org/10.5281/zenodo.1255306}
%\textbf{link for online repository 1}
%and
%remove author identification for double-blind review process
%\href{https://github.com/pinga-lab/use-the-disturbance}{github.com/pinga-lab/use-the-disturbance}
%\textbf{link for online repository 2}.
